Dirac neutrino mass generation from Majorana messenger

### 2019-07-27 draft.tex
Updates from Overleaf

\section{Introduction}
\label{sec:intro}
%Dirac vs Majorana (From previous paper: must be rephrased
The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the number the effective
number light neutrinos, $N_{\text{eff}}$, until 6. To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked.

Discussion: At three level seem to have that we can have also all Majorana mediators for Dirac neutrinos. See plot:

\includegraphics[scale=0.5]{tl}

% Tree-level see-saw with fermionic mediators: Dirac for Dirac, Majorana-Majorana
% One-loop level: Majorana-Majorana, Dirac-Dirac, Majorana-Dirac. Simplest model with Dirac-Majorana still missing
% At one-loop Dark Matter is predicted in model-dependent ways. In this case...

The standard model (SM) does not explain the neutrinos mass predicted by the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}. From neutrino oscillation experiments, we know that at least two neutrinos must be massive and their respective mixing angles~\cite{deSalas:2017kay}. The experiments still do not determine if the neutrinos are Dirac or Majorana particles, since the double beta decays are not yet conclusive~\cite{Arnold:2016bed, Albert:2017owj, Alduino:2017ehq, Aalseth:2017btx, Agostini:2018tnm, KamLAND-Zen:2016pfg}.

In the SM all fermions acquire masses through a Dirac term, it is natural to believe that neutrinos acquire masses in this way, so there are some studies that develop this hypothesis~\cite{Branco:1978bz}. If the neutrinos are  Dirac, this establishes a physics beyond SM (BSM), this predicts the existence of at least two right-handed neutrinos. If neutrino mass is generated at tree level, establishes that Yukawas must be very small ($\lesssim 10^{-10}$) to explain tiny neutrino masses~\cite{deSalas:2017kay}. So it is preferred to generate the masses through mechanisms that develop in a loop~\cite{Branco:1978bz, Zee:1980ai, Ma:2006km}.

In some models to forbidden terms of Dirac at tree level and Majorana terms, discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}. In recent works, using symmetry ($B-L$) to forbid these terms without resorting to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}. In these cases, it is necessary to introduce new scalars and new dirac or vector-like fermions, that are used for to close the loop.

Another evidence that SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM). The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}. We will make use of the scotogenic model~\cite{Ma:2006km}. In scotogenic model the neutrino masses and the DM have common explanation. The mass of the neutrinos is generated to one-loop, where the mediators in the loop are viable candidates for DM.

In this work we propose a model with Dirac neutrinos at one-loop, in which the mediators are Majorana fermion and one singlet scalar and one doublet scalar. This mediators can to be dark matter candidates. Additionally, for generated neutrino mass is necessary to add a second Higgs doublet. The rest of the paper is organized as follows. In the next section we present the model and the particle content. In the section~\ref{sec:ScaMassSpect} we study the scale mass spectrum after spontaneous symmetry breaking. In section~\ref{sec:Neutrinos} we present the mechanism that generates the neutrino masses. In section~\ref{sec:LFV} we show the experimental lepton flavor violation (LFV) constrains. Finally, in the section~\ref{sec:DM} we present the viable DM candidates.

\section{The model}
\label{sec:Model}
As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $. The two doublets are coupling differently to the fermions, the first doublet is coupled to quarks up-type and the charged leptons, while the second doublet is coupled to down-type quarks. To forbid another terms, we used a $U(1)^{\prime}$ symmetry. This model is known as two Higgs doublets model type II (2HDM-II)~\cite{Davidson:2005cw}. Also, these symmetry allows us to forbid Dirac mass terms at tree level. Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$. The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the Yukawa interactions. In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

The most general Yukawa Lagrangian is:
%
\begin{align*}
\label{Eq:LagY}
    \mathcal{L} \subset& -[ 
    h^{a}_{i} \overline{L_{i}} \psi_{a} \widetilde{\eta}  +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S^{*} + h.c.] \\
    &- \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)\,,
\end{align*}
%
where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{*}$ and $\mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)$ is the scalar potential. $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
%
\begin{table}
  \centering
  \begin{tabular}{|l|l|l|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
    $H_{d} $  & $(2,-1/2)$ &  2 \\
    $H_{u} $  & $(2, 1/2)$ &  0 \\
    $\eta$ & $(2,1/2)$ & $-1$ \\
    $S$ & $(1,0)$ & $-2$ \\
    $\sigma$ & $(1,0)$ & $-3$ \\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $-2$ \\
    \hline
    $L_i$  & $(2,-1/2)$ & $0$ \\
    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges.}
  \label{tab:partcont}
\end{table}
%

The most general gauge invariant scalar potential for this model is
%
\begin{align*}
    \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma) = & \mathcal{V}(H_{u}) + \mathcal{V}(H_{d}) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
    &+ \lambda_{1} (H^{\dagger}_{u} H_{u}) (H^{\dagger}_{d} H_{d}) + \lambda_{2} (H^{\dagger}_{u} H_{d}) (H^{\dagger}_{d} H_{u}) + \lambda_{3} (H_{u}^{\dagger} H_{u} ) (S^{*} S) + \lambda_{4} (H_{u}^{\dagger} H_{u} ) (\sigma^{*} \sigma ) \\
    &+ \lambda_{5} (H_{u}^{\dagger} H_{u} ) (\eta^{\dagger} \eta ) + \lambda_{6} (H_{d}^{\dagger} H_{d} ) (S^{*} S) + \lambda_{7} (H_{d}^{\dagger} H_{d} ) (\sigma^{*} \sigma ) + \lambda_{8} (H_{d}^{\dagger} H_{d} ) (\eta^{\dagger} \eta )  \\
    &+ \lambda_{9} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{10} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{12} (\eta^{\dagger} H_{u} ) (H^{\dagger}_{u} \eta ) \\
    &+ \lambda_{13} (\eta^{\dagger} H_{d} ) (H^{\dagger}_{d} \eta ) + (\mu \epsilon_{a b} H_{d}^{a} \eta^{b} \sigma + \mu_{1} \widetilde{H^{\dagger}_{d}} H_{u} S + \text{h.c.})\,,
\end{align*}
%
where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$. We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.

@@

 After spontaneous symmetry breaking, both Higgs doublet and scalar $S$ can to acquire vev's
%
\begin{align*}
    H_{u} =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
    &H_{d} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
    &\eta =& \begin{pmatrix}\eta^{+} \\ \eta^{0} \end{pmatrix} \,,
\end{align*}
%
with $\eta^{0} = (\eta_{1}^{0}+i \eta_{2}^{0})/\sqrt{2}$ and $\sigma = ({\sigma}_{1}+i {\sigma}_{2})/\sqrt{2}$ and $\langle  H_{i} \rangle = \upsilon_{i}$ with $\upsilon=\sqrt{\upsilon_{1}^2+\upsilon_{2}^2} \simeq 246$\,GeV. It's possible to parameterize the ratio of these vev's as $\tan \beta = \upsilon_{2}/\upsilon_{1}$.

With the minimum of the scalar potential it is possible to write $\mu_{H_{u}}^{2}$,$\mu_{H_{d}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
%
\begin{align*}
    \mu^{2}_{H_{u}} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H_{u}} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{d}}}{\upsilon^{2}}+\lambda_{H_{d}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{d}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{d}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{d}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{d}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
\end{align*}
%
where $t_{\beta} = \tan \beta$, $c_{\beta} = \cos \beta$ and $s_{\beta} = \sin \beta$. This allows to reduce the number of free parameters.

Of the original sixteen scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G^{0}$ and $G^{\prime}$). There are two physical neutral CP-even Higgs state ($H$ and $h$, where $m_{H} \geq m_{h}$), one scalar state ($\phi$), one physical CP-odd Higgs scalar ($A^{0}$), two CP-even scalar state ($\sigma_{1}$ and $\eta^{0}_{1}$), two CP-odd scalar state ($\sigma_{2}$ and $\eta^{0}_{2}$), one charged scalar pairs ($\eta^{\pm}$) and one charged Higgs pairs ($h^{\pm}$). The mass spectrum for the scalar sector is given by
\begin{align*}
    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{d}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{d}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{5} \upsilon^{2}_{1} + \lambda_{8} \upsilon^{2}_{2} + \lambda_{10} \upsilon^{2}_{s} )\,, \\
    m_{A^{0}}^{2} &= m_{h^{\pm}}^{2} + \frac{1}{2} \lambda_{2} \upsilon^{2}_{1} \,,
\end{align*}
%
note that the two charged scalars do not mix among themselves. The neutral mass eigenstate are defined as
%
\begin{align*}
    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(1,2)} \\ \eta_{(1,2)} \end{pmatrix} \,,
\end{align*}
%
where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{4} \upsilon^{2}_{1} + \lambda_{7} \upsilon^{2}_{2} + \lambda_{9} \upsilon^{2}_{s})$\,,
$b = \mu^{2}_{\eta^{\pm}} + \frac{1}{2}(\lambda_{12} \upsilon^{2}_{1} + \lambda_{13} \upsilon^{2}_{2})$ and $c = \mu \upsilon_{2}/\sqrt{2}$\,. The corresponding mass eigenvalues are
\begin{align*}
    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c} \right)\,, \\
     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c} \right)\,,
\end{align*}

@@

For the Dirac neutrinos the mass matrices are diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} M_{\nu_{D}} U^{(\nu)}_L = M_{\nu_{D}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstate, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can to express the Dirac neutrino mass matrix following way
\begin{align}
(M_{\nu_{D}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{D}}^{\text{diag}})_{jj}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles.

@@

\section{Cosmological constrain}
\begin{comment}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Tdec.pdf}
\includegraphics[scale=0.6]{Delta_Neff1.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:Neff}
\end{figure}
%
\end{comment}

>>>>

\section{Introduction}
\label{sec:intro}

The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino masses
\cite{Tanabashi:2018oca}. The former possibility has received the most
attention but, given the lack of signals in neutrinoless double beta
decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
the latter cannot be dismissed. If neutrinos are Dirac particles, the
Standard Model (SM) particle content must be extended with
right-handed neutrinos, which can increase the effective
number of light neutrinos, $N_{\text{eff}}$, until 6. 
To be compatible with the current cosmological restrictions on
$N_{\text{eff}}$, only the  ps w l therm
To give small
masses to at least two Majorana or Dirac neutrinos, as required to
explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
invoked. For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}. The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}. In this
work we want to explore the possibility to build a simple model with Dirac neutrino
masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.

In models for Dirac neutrinos with some explanation for the smallness of
their masses, usually an adhoc discrete symmetry is invoked to forbid
the SM induced terms of Dirac at tree level and Majorana terms,
and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
In recent works, using symmetry ($B-L$) to forbid these terms without resorting
to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
In these cases, it is necessary to introduce new scalars and new Dirac or 
vector-like fermions, that are required to close the loop.

Another evidence that SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM). The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}. We will make use of the scotogenic model~\cite{Ma:2006km}. In scotogenic model the neutrino masses and the DM have common explanation. The neutrino masses are generated by one-loop effects, where the candidates for DM are mediators in the loop.

In this work we propose a Dirac radiative type-I seesaw,
with Majorana fermion of the mediators in the loop.. This mediators can to be DM candidate. The rest of the paper is organized as follows. In the next section we present the model and the particle content. In the section~\ref{sec:ScaMassSpect} we study the scalar mass spectrum after spontaneous symmetry breaking. In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses. In section~\ref{sec:LFV} we show the lepton flavor violation (LFV)experimental  constraints. Finally, in the section~\ref{sec:DM} we present the viable DM candidates.

\section{The model}
\label{sec:Model}
As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $. To forbid another terms, we used a $U(1)^{\prime}$ symmetry. This model is known as two Higgs doublets model (2HDM)~\cite{Davidson:2005cw}. Also, these symmetry allows us to forbid Dirac mass terms at tree level. Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$. The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the Yukawa interactions. In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

The most general Yukawa Lagrangian is:
%
\begin{align*}
\label{Eq:LagY}
    \mathcal{L} \subset& -[ 
    h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
    &- \mathcal{V}(H, H_{2}, S, \eta, \sigma)\,,
\end{align*}
%
where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, H_{2}, S, \eta, \sigma)$ is the scalar potential. $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
%
\begin{table}
  \centering
  \begin{tabular}{|l|l|l|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
    $H $  & $(2, 1/2)$ &  0 \\
    $\eta$ & $(2,1/2)$ & $1$ \\
    $S$ & $(1,0)$ & $2$ \\
    $\sigma$ & $(1,0)$ & $3$ \\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
    \hline
    $L_i$  & $(2,-1/2)$ & $0$ \\
    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges.}
  \label{tab:partcont}
\end{table}
%

The most general gauge invariant scalar potential for this model is
%
\begin{align*}
    \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
    &+  \lambda_{3} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{4} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{5} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
    &+ \lambda_{9} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{10} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{12} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
    &+ (\mu \eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
\end{align*}
%
where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$. We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.

@@

 After spontaneous symmetry breaking, both Higgs doublet and scalar $S$ can to acquire vev's
%
\begin{align*}
    H =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
    &H_{2} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
    &\eta =& \begin{pmatrix}\eta^{+} \\ \eta^{0} \end{pmatrix} \,,
\end{align*}
%
with $\eta^{0} = (\eta_{1}^{0}+i \eta_{2}^{0})/\sqrt{2}$ and $\sigma = ({\sigma}_{1}+i {\sigma}_{2})/\sqrt{2}$ and $\langle  H_{i} \rangle = \upsilon_{i}$ with $\upsilon=\sqrt{\upsilon_{1}^2+\upsilon_{2}^2} \simeq 246$\,GeV. It's possible to parameterize the ratio of these vev's as $\tan \beta = \upsilon_{2}/\upsilon_{1}$.

With the minimum of the scalar potential it is possible to write $\mu_{H}^{2}$,$\mu_{H_{2}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
%
\begin{align*}
    \mu^{2}_{H} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{2}}}{\upsilon^{2}}+\lambda_{H_{2}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{2}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{2}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{2}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{2}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
\end{align*}
%
where $t_{\beta} = \tan \beta$, $c_{\beta} = \cos \beta$ and $s_{\beta} = \sin \beta$. This allows to reduce the number of free parameters.

Of the original sixteen scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G^{0}$ and $G^{\prime}$). There are two physical neutral CP-even Higgs state ($H$ and $h$, where $m_{H} \geq m_{h}$), one scalar state ($\phi$), one physical CP-odd Higgs scalar ($A^{0}$), two CP-even scalar state ($\sigma_{1}$ and $\eta^{0}_{1}$), two CP-odd scalar state ($\sigma_{2}$ and $\eta^{0}_{2}$), one charged scalar pairs ($\eta^{\pm}$) and one charged Higgs pairs ($h^{\pm}$). The mass spectrum for the scalar sector is given by
\begin{align*}
    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{2}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{2}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{5} \upsilon^{2}_{1} + \lambda_{8} \upsilon^{2}_{2} + \lambda_{10} \upsilon^{2}_{s} )\,, \\
    m_{A^{0}}^{2} &= m_{h^{\pm}}^{2} + \frac{1}{2} \lambda_{2} \upsilon^{2}_{1} \,,
\end{align*}
%
note that the two charged scalars do not mix among themselves. The neutral mass eigenstate are defined as
%
\begin{align*}
    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(1,2)} \\ \eta_{(1,2)} \end{pmatrix} \,,
\end{align*}
%
where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{4} \upsilon^{2}_{1} + \lambda_{7} \upsilon^{2}_{2} + \lambda_{9} \upsilon^{2}_{s})$\,,
$b = \mu^{2}_{\eta^{\pm}} + \frac{1}{2}(\lambda_{12} \upsilon^{2}_{1} + \lambda_{13} \upsilon^{2}_{2})$ and $c = \mu \upsilon_{2}/\sqrt{2}$\,. The corresponding mass eigenvalues are
\begin{align*}
    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c} \right)\,, \\
     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c} \right)\,,
\end{align*}

@@

For the Dirac neutrinos the mass matrices are diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} M_{\nu_{2}} U^{(\nu)}_L = M_{\nu_{2}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstate, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can to express the Dirac neutrino mass matrix following way
\begin{align}
(M_{\nu_{2}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{2}}^{\text{diag}})_{jj}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles.

@@

\section{Cosmological constraints}
\begin{comment}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Tdec.pdf}
\includegraphics[scale=0.6]{Delta_Neff1.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:Neff}
\end{figure}
%
\end{comment}

%
\begin{table}
  \centering
  \begin{tabular}{|l|l|c|c|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)_{L}$& $Z_2$\\ \hline
    $H $  & $(2, 1/2)$ &  0 &$+$\\
    %$\widetilde{H_{2}}$  & $(2,1/2)$ &  $0$ &$-$\\
    $\eta$ & $(2,1/2)$ & $1-\psi\to 5/2$ &$-$\\
    $S$ & $(1,0)$ & $-2\psi\to 3$ &$+$\\
    $\sigma$ & $(1,0)$ & $\nu+\psi=\eta=1-\psi\to 5/2$&$-$\\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$& $+$\\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$& $+$\\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$& $+$\\
    \hline
    $L_i$  & $(2,-1/2)$ & $-1$& $+$\\
    $\overline{e_{R_i}}$ & $(1,1)$ & $+1$ & $+$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $\nu\to 1-2\psi\to 4$&$+$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $\nu_k$&$+$\\
    $\psi_{i}$  & $(1,0)$ & $\psi\to -3/2$ &$-$\\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges. $Z_2$ to define THDM Type-II~\cite{1303.0168}}
  \label{tab:partcont}
\end{table}
%
